Finch: Sparse and Structured Array Programming with Control Flow

### 2024-04-04 sections/intro.tex
Update on Overleaf.

This advances the state-of-the-art over the Looplets work. While Looplets presented a way to merge iterators over multiple single dimensional structures, we go further combine single-dimensional looplet structures into multi-dimensional tensors and operate on them in a programming language with fully-featured control flow.

>>>>

This advances the state-of-the-art over the Looplets work. While Looplets presented a way to merge iterators over multiple single dimensional structures, we go further, combining single-dimensional looplet structures into multi-dimensional tensors and operate on them in a programming language with fully-featured control flow.
